### 2011-09-16 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress

@@

TODO we will try 3 different scenarios, see which performs the best on the data and then try to tweak it a bit.

@@

TODO result graphs

@@

TODO choose the best

TODO experiment to try to improve the best

>>>>

% TODO I cannot stress this enough times: make sure there is an explanation of heuristics notation used in pseudocode listing, SOMEWHERE

@@

TODO we will try 3 different scenarios, see which performs the best on the data and then try to tweak it a bit. First we set all ratios to 0.1, as soon as we find the best scenario, we will tweak it.

@@

TODO result graphs - just a \textbf{commented} sample

@@

TODO choose the best - see how many times in the 20 runs did they find optimum

             1       2      3
100-100      20      19     20
100-200      19      18     17
100-1000     4       1      5
OVA1         20      20     20
OVA2         19      13     18
OVA3         17      18     20

Strategies 1 and 3 are very similar, we shall choose \textbf{1} for its simplicity to tune the parameters.

\subsubsection{Improving Strategy 1}

TODO remind what Strategy 1 is, list all ratios we will be using, list files we will be using.

TODO we will be gathering for each run the following: what were the parameters, how long did it take and whether it found optimum

TODO summary table

TODO results and interpretation

RR = 0.5 (strong diversification), MUT = 0.05 (only a few fixed), CX = 0.2 (looking for commonalities among 1/5th of the pool)
